---
title: "Case Study"
author: "Kaleb J. Frierson"
date: "2024-10-08"
output: html_document
---

# Notes

Recurring themes in data science:

You need some data skills: wrangling, reproducibility, communication, analytics/modeling. These have been the focus of this course. However, you also need a mindset guided by intellectual curiosity, an ability to solve problems, and an interest in domain.

What is domain?

You can practice problem solving!

# Coding

## Library Calling and Format Setting

```{r}
library(tidyverse)
library(haven)
library(leaflet)
```

## Bringing in Data

```{r}
bnb =
  read.csv("nyc_airbnb.csv", na = c("NA", "", "."))

```

## Questions about data

-   Where are max and min air bnb prices?
    -   What are average prices?
    -   What factors affect prices?

```{r, mean by borrough}
bnb |> 
  group_by(neighbourhood_group) |>
  summarize(
    mean(price),
    median(price)
  )
```

```{r, count of units by price in each borrough graph}
bnb |> 
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() +
  facet_grid(. ~ neighbourhood_group) +
  scale_x_continuous(limits = c(0, 250))
```

-   Where are prices going up and down over time?

-   What is the relationship between number of reviews and average reviews?

```{r}
bnb |> 
  ggplot(aes(x=number_of_reviews, y=review_scores_location)) + 
  geom_point()
```

-   Does room type effect availability?

-   What area's are popular?

    -   Popularity = number of units? Average price? How to measure?

```{r}
bnb |> 
  filter(neighbourhood_group == "Manhattan",
  price <1000) |> 
  ggplot(aes(x= lat, y = long, color = price))+
  geom_point(alpha = .1)
```

```{r}
bnb |> 
  filter(neighbourhood_group == "Manhattan",
  price <1000,
  room_type == "Entire home/apt") |> 
  group_by(neighbourhood) |> 
  summarize(mean_price = mean(price)) |> 
  arrange(mean_price)
```

-   Repeat hosts?
    -   If so, what odes that mean?

## Leaflet maps 
leaflet works very similar to ggplot (I think for making maps)

```{r}
bnb |>
  filter(neighbourhood_group == "Manhattan",
  price <1000) |> 
  slice(1:100) |> 
  leaflet() |> 
  addTiles() |> 
  addCircleMarkers(~lat, ~long, radius=.5)
```

You can checkout rstudio.github.io for help learning this too. 


